Highlights

### 2021-08-23 Bike-share-spatial-equity/Highlights.Rmd
Final draft of Highlights for submission
Revised Highlights - June 2021

* Balanced floating catchment area methods are applied to measure accessibility to PBSP

* Contribution of equity stations to accessibility assessed at different thresholds

* Equity stations increase accessibility modestly for all income groups

* Lowest income group has lowest levels of accessibility, even with equity stations

* Locations for new stations are identified to increase equitable access to PBSP

>>>>

* Balanced floating catchment area method applied to measure accessibility to bikeshare

* Contribution of stations added to increase equity assessed at different thresholds

* Added stations increased accessibility and reduced inequities, albeit only modestly

* Lowest income group has lowest levels of accessibility, even with "equity" stations

* Location and size of docking stations matters for increasing equity in accessibility
